CRUSE to Safe Cycling in Ireland

### 2023-10-03 paper.qmd
Describe Near Market

- Domestic with cycle trips starting at home
- Domestic trips involving travel by other mode to the start of the cycle trip
- Cycle tourism, where start and end trips are different
- Sport cycling 
-->
```
## Routing

@@

The Baseline scenario approximates current cycling levels.
As outlined

Near market Climate Action Plan Go Dutch Ebike

>>>>

- Domestic with cycle trips starting at home
- Domestic trips involving travel by other mode to the start of the cycle trip
- Cycle tourism, where start and end trips are different
- Sport cycling 
-->
```

## Routing

@@

The Baseline scenario approximates current cycling levels.
As outlined in @sec-trip-purposes, the Baseline scenario includes travel to work and school, and additional trip purposes.
Cycling levels were taken from the POWSCAR data, which includes the number of people travelling by each mode between each OD pair.

The Near Market scenario approximates the level of cycling that would be achieved if levels of cycling uptake observed in areas of Ireland with high levels of cycling according to the 2016 Census were achieved everywhere, accounting for differences in trip distances and hilliness levels.
The scenario is implemented as follows:

-   Calculate distance decay curves for Dublin for the base year (2016, using POWSCAR data) by fitting a model to the relevant OD data after it has been converted to a route network datasest
-   Apply the Near Market model to the hilliness and distance values for each county during the build process
-   Add the current level of cycling to the Near Market model

An illustration of the level of cycling under various scenarios in the county of Limerick is shown in Figure \@ref(fig:distance-frequency).
The results will vary from county to county.

 Climate Action Plan Go Dutch Ebike
